%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Dan Shipper
\documentclass[margin,line]{resume}
\usepackage{color}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Dan Shipper}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    262 Upper Ferry Road,          \hfill mobile: 609-933-6872          \vspace{0mm}\\\vspace{0mm}%           
    Ewing, NJ 08628                    \hfill e-mail: dan@danshipper.com  \vspace{0mm}\\\vspace{-4.5mm}% 
					     \hfill website: danshipper.com  \vspace{0mm}\\\vspace{-2.5mm}%      
     

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Pennsylvania}, Philadelphia, PA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Intended major in Computer Science} \hfill \textbf{ September 2010 -- present}\vspace{-5mm}%
        
        GPA of 3.85 / 4.00. SAT: 2270\\
        Expected graduation date: May 2014

    %__________________________________________________________________________________________________________________
    % Technical Experience
    \section{\mysidestyle Technical\\Experience}
    
     \textbf{WhereMyFriends.Be} \hfill \textbf{February 2011}\vspace{-3mm}%
     
     A viral mashup of the Google Maps API and the Facebook API that shows a map of all your friends around the world. Built with PHP, Javascript and MySQL, it was featured on \textbf{Mashable.com} and \textbf{CNN.com} and received very positive feedback. We have received almost 30,000 signups and mapped over 3,000,000 friends to date.

    \textbf{OneSmallPage.com} \hfill \textbf{January 2011}\vspace{-3mm}%
     
     A web app built in Python that allows you to pick an out of copyright book and have up to five pages of that book sent to your email every day.


    \textbf{Convenience Software} \hfill \textbf{May 2009 -- May 2010}\vspace{-3mm}%
     
     I started Convenience Software in November of 2007 to provide a place to market and distribute pieces of software that I had been writing since I became interested in programming in 5th grade.  I currently sell a number of products for BlackBerry and the iPhone, including GetItBack for BlackBerry, which allows its user to track and retrieve a lost or stolen BlackBerry through a web-interface.


    %__________________________________________________________________________________________________________________
    % Leadership Experience
    \section{\mysidestyle Leadership\\Experience}

     \textbf{President of the Senior Class} \vspace{2mm}\\\vspace{1mm}%
     \textsl{High School} \hfill \textbf{May 2009 -- May 2010}\\
     As President of the Senior Class it is my job to run class meetings, represent my class during Community Council, and carry out various other duties such as organizing class trips, planning for the Commencement Speaker, and communicating with the school administration about various class issues and activities.

    \textbf{Editor-in-Chief of the Spokesman}\vspace{2mm}\\\vspace{1mm}%
    \textsl{High School Newspaper} \hfill \textbf{March 2009 -- March 2010}\\
    The Spokesman is the monthly school newspaper of Princeton Day School. There are eight issues released during an Editor-in-Chief’s tenure.  I envisioned and helped to produce a Spokesman Article Management Interface which is a website that allowed our editors to keep track of articles and pieces of art within the production cycle.  Additionally, I worked to create the Spokesman’s public website which became available in October 2009. It is available at {\color{blue} http://spokesman.pds.org.}

    \textbf{Systems Operator} \vspace{2mm}\\\vspace{1mm}%
    \textsl{High School} \hfill \textbf{May 2007 -- May 2010}\\
     As a Systems Operator (SysOp) it was my job to moderate my high school's email system, PDSNet, and to remove any obscene or offensive material from it.  Additionally, I was required to assist teachers and students with technology issues such as printing problems, or projector issues.

    \textbf{Publicity Director} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Junior State of America} \hfill \textbf{May 2009 -- May 2010}\\
     After I was elected my Junior State of America Chapter’s Publicity Director, I organized the first JSA teacher debate on the topic of Gay Marriage.  The event, which I created buzz for in a number of ways including producing a short teaser video, drew upwards of seventy people, the most ever for a JSA debate at PDS, and was a resounding success.





    %__________________________________________________________________________________________________________________
    % Programming
    \section{\mysidestyle Programming} 

   PHP, MySQL, Javascript, Python, Ruby on Rails, Java, C/C++, \LaTeXe.




%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

